---
title: "R Project 1 - Hello R"
author: "Hasan Khan"
date: "Due Sep 8th"
output: 
  html_document: 
    fig_width: 11
    fig_height: 9
    highlight: kate
    theme: sandstone
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

datasaurus_dozen file has 1846 rows and 3 columns.

The 3 variables are 

1. dataset

2. x: x values

3. y: y values

### Exercise 2


```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

```{r plot-star, fig.height=3, fig.width=6}
dino_data<- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

 
```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```
```

r of star is greater than the r of dino

```
### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r plot-circle, fig.height=7, fig.width=4}
dino_data<- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()


```

```{r cor-circle}
dino_data %>%
  summarize(r = cor(x, y))


```
``` 
r of circle is smaller than that of dino

```

### Exercise 5

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) 
```
```{r}
datasaurus_dozen %>% group_by(dataset) %>% 
  summarize(r = cor(x, y)) %>%
  print(26)
```


